Revision Plan for SIGCOMM'24 Paper \#293

### 2024-06-04 revision_plan.tex
update proposed modification

@@

@@

\noindent\textcolor{blue}{\textbf{Response 3:} 
PPT's performance benefits are steamed from the following points. First, DCTCP contains spare bandwidth in slow start phase, which is obvious.
Second, in queue build-up phase, DCTCP also contains some spare bandwidth. We have already shown this point using a preliminarily experiment in Fig.1. But the reviewer may consider this experiment only contains synchronized bursts. Actually, in this experiment, the flows are generated according to Poisson arrival  pattern. So, there are both synchronized and nonsynchronized cases. We plan to clarify this point in our paper.
Finally, PPT uses a mirror-symmetric packet tagging design. This makes PPT achieve comparable performance on the average FCT of small flows.
}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
We actually are not claiming that ``integration with other transports is easy".
What we claim is that the design of PPT can be integrated with delay-based transport.
We have already justified this point in our submission.
First, we have already implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator and showed that PPT's design can improve the performance of the original delay-based transport. Please see Fig. 26 for more details.
On the other hand, we have also discussed about the compatibility of PPT with other transports. Please see Appendix A for more details.
}

@@

\noindent\textcolor{blue}{\textbf{Response 5:}
We will complete the missing details about the experimental setup and parameters in the form of tables.
%We record the maximum value of the window from the beginning of the flow until now as MW (Maximum Window).
%Section 2.3 first shows how much DCTCP can benefit from padding the spare bandwidth to MW and plots the results in Figure 2.
%Moreover, we show that padding the spare bandwidth to MW is just suitable without wasting bandwidth or causing congestion throughout the experiment, and we plot the results of our experiment in Figure 3.
%Another question is about specific TCP send buffer thresholds.
%To reproduce the behavior of the actual deployed application as much as possible, we selected specific application traces for the Memcached application and the web server application, respectively.
%The flow size distribution in specific application traces is concentrated in particular intervals, e.g., there is no flow in the ETC trace of the paper[8] that exceeds 100KB.
%Under such traces, we set different thresholds depending on the traces to verify the effectiveness of the buffer-aware flow identification.
%In the large-scale simulation and testbed, the TCP send buffer threshold is set to the fixed value of 100KB, with outstanding results.
%To evaluate if this can benefit PPT’s performance, we construct a PPT variant that turns off this approach and considers all flows non-identified.
%We plot the results in Figure 20, showing that this improves the small flow performance as expected.
%In summary, the TCP send buffer threshold does not assume that the application type and flow size distribution are known a priori and effectively improves small flow performance.
}

@@

@@

@@

@@

@@

\textcolor{blue}{
On the other hand, PPT will open an LCP loop for each of the flow in flows 2$\sim$11 (if they are identified as small flows) to let them send opportunistic packets. However, these opportunistic packets may be queued or dropped due to buffer overflow, thus their LCP loops will be closed in a short while.
} 
%PPT actually will not send the opportunity packet when 10 more flows arrive.
%Specifically, traffic bursts result in more ECN-marked packets.
%The value of $\alpha$ increases due to Eq. (1), when PPT will not send any opportunity packets.

@@

%\noindent\textcolor{blue}{\textbf{Response A.2:}
%Thanks for the reviewer's comments. 
%At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end."
%Therefore, HCP and LCP send packets from the beginning and end of the same flow, respectively.
%So, there is no scenario in which there is no HCP flow.
%Since HCP and LCP come from the same flow, they must have the same number and destination.
%}

@@

@@

@@

@@

%\noindent\textcolor{blue}{\textbf{Response C.1:}
%Thanks for the reviewer’s comments. 
%Indeed, in section 2.3, we mention that \emph{DCTCP marks ECN at the switch for arriving packets if queue occupancy exceeds a threshold K, and the sender cuts the window based on the fraction of ECN marked ACKs. So, when there are multiple concurrent flows, DCTCP may mark ECN for packets from many flows, which may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized.}
%To show this point, We run ns-3 simulations with two senders and one receiver sharing the bottleneck. 
%We sample the bottleneck link utilization every 100us for 10ms when DCTCP enters a steady state.
%We plot the results in Figure 1, showing that nearly half of the bandwidth is underutilized.
%}

@@

@@

@@

@@

@@

>>>>

\noindent\textcolor{red}{\textbf{Proposed modification: }
Our experiments indeed demonstrate that our approach delivers comparable performance to proactive transports while remaining readily deployable. Therefore, we will not add further explanations or analyses in the paper. To address the reviewers' possible misunderstandings regarding the flow scheduling scheme, we will add an analysis under the title of section 4 on the page 6 and include additional explanations in the footnotes on the page 7.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We plan to discuss PCC Proteus and other related work in the related work section on page 12.
}

@@

\noindent\textcolor{blue}{\textbf{Response 3:} 
PPT's performance benefits are steamed from the following points. First, DCTCP contains spare bandwidth in slow start phase, which is obvious.
Second, in queue build-up phase, DCTCP also contains some spare bandwidth. We have already shown this point using a preliminarily experiment in Fig.1. But the reviewer may consider this experiment only contains synchronized bursts. Actually, in this experiment, the flows are generated according to Poisson arrival  pattern. So, there are both synchronized and nonsynchronized cases. We plan to clarify this point in our paper.
Finally, PPT uses a mirror-symmetric packet tagging design. This makes PPT achieve comparable performance on the average FCT of small flows.
}
\noindent\textcolor{red}{\textbf{Proposed modification: }
We will show more insights in Section 2.3 on page 4.
}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
We actually are not claiming that "integration with other transports is easy".
What we claim is that the design of PPT can be integrated with delay-based transport.
We have already justified this point in our submission.
First, we have already implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator and showed that PPT's design can improve the performance of the original delay-based transport. Please see Fig. 26 for more details.
On the other hand, we have also discussed about the compatibility of PPT with other transports. Please see Appendix A for more details.
}

\noindent\textcolor{red}{\textbf{Proposed modification: }
Given our analysis, we will not add further explanations in the paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response 5:}
We will complete the missing details about the experimental setup and parameters in the form of tables.
}

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will add a table to fill in the missing parameters in the appendix on page 19.
}
%We record the maximum value of the window from the beginning of the flow until now as MW (Maximum Window).
%Section 2.3 first shows how much DCTCP can benefit from padding the spare bandwidth to MW and plots the results in Figure 2.
%Moreover, we show that padding the spare bandwidth to MW is just suitable without wasting bandwidth or causing congestion throughout the experiment, and we plot the results of our experiment in Figure 3.
%Another question is about specific TCP send buffer thresholds.
%To reproduce the behavior of the actual deployed application as much as possible, we selected specific application traces for the Memcached application and the web server application, respectively.
%The flow size distribution in specific application traces is concentrated in particular intervals, e.g., there is no flow in the ETC trace of the paper[8] that exceeds 100KB.
%Under such traces, we set different thresholds depending on the traces to verify the effectiveness of the buffer-aware flow identification.
%In the large-scale simulation and testbed, the TCP send buffer threshold is set to the fixed value of 100KB, with outstanding results.
%To evaluate if this can benefit PPT’s performance, we construct a PPT variant that turns off this approach and considers all flows non-identified.
%We plot the results in Figure 20, showing that this improves the small flow performance as expected.
%In summary, the TCP send buffer threshold does not assume that the application type and flow size distribution are known a priori and effectively improves small flow performance.

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will add more text under the title of section 4 on page 6 and include additional explanations in the footnotes on page 7.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will not provide further explanations on this concern in the paper.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We plan to discuss PCC Proteus in the related work section on page 12.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
Given our analysis, we will not add further explanations in the paper.
}

@@

\textcolor{blue}{
On the other hand, PPT will open an LCP loop for each of the flow in flows 2$\sim$11 (if they are identified as small flows) to let them send opportunistic packets. However, these opportunistic packets may be queued or dropped due to buffer overflow, thus their LCP loops will be closed in a short while.
}

\noindent\textcolor{red}{\textbf{Proposed modification: }
Given our analysis, we will not add further explanations in the paper.
}
%PPT actually will not send the opportunity packet when 10 more flows arrive.
%Specifically, traffic bursts result in more ECN-marked packets.
%The value of $\alpha$ increases due to Eq. (1), when PPT will not send any opportunity packets.

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
To address the reviewers' possible misunderstandings regarding the flow scheduling scheme, we will add an analysis under the title of section 4 on page 6 and include additional explanations in the footnotes on page 7.
}
%\noindent\textcolor{blue}{\textbf{Response A.2:}
%Thanks for the reviewer's comments. 
%At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end."
%Therefore, HCP and LCP send packets from the beginning and end of the same flow, respectively.
%So, there is no scenario in which there is no HCP flow.
%Since HCP and LCP come from the same flow, they must have the same number and destination.
%}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
Based on the above analysis, we will not add further explanations in the paper.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will add an analysis in the future work section on page 12.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will add a new simulation with 100/400G topology to demonstrate this point. The results and analysis of this experiment will be presented in Appendix C on page 18 of the paper.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will show more details and analysis in Section 2.3 on page 4.
}
%\noindent\textcolor{blue}{\textbf{Response C.1:}
%Thanks for the reviewer’s comments. 
%Indeed, in section 2.3, we mention that \emph{DCTCP marks ECN at the switch for arriving packets if queue occupancy exceeds a threshold K, and the sender cuts the window based on the fraction of ECN marked ACKs. So, when there are multiple concurrent flows, DCTCP may mark ECN for packets from many flows, which may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized.}
%To show this point, We run ns-3 simulations with two senders and one receiver sharing the bottleneck. 
%We sample the bottleneck link utilization every 100us for 10ms when DCTCP enters a steady state.
%We plot the results in Figure 1, showing that nearly half of the bandwidth is underutilized.
%}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will revise it on page 11.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will add more intuitive reasons in Section 6.2 on page 11.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We plan to discuss Swift and Timely in the related work on page 12 and show more details about the actual algorithm in the footnotes on page 17.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
Given our shown result, we will not add further explanations in the paper.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
Due to time constraints, we will not add further experiment in the paper.
}
